---
title: "Predict faithful eruption"
date: "April 18 2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Explore Data
```{r faithful, echo = FALSE}
head(faithful)
summary(faithful)
```

## Plot waiting and eruption duration
```{r}
plot(faithful$waiting, faithful$eruptions,  xlab = "Waiting Time", 
             ylab = "Duration", bty = "n", pch = 16,
             xlim = c(40, 100), ylim = c(1, 6))
```

## Predict model 
model <- lm(eruptions ~ waiting, data = faithful)

```{r}
plot(faithful$waiting, faithful$eruptions,  xlab = "Waiting Time", 
             ylab = "Duration", bty = "n", pch = 16,
             xlim = c(40, 100), ylim = c(1, 6))
model <- lm(eruptions ~ waiting, data = faithful)
abline(model, col = "red", lwd = 2)

```

## Description


- This project uses R default dataset: faithful
- It builds a model to predict the eruption duration by waiting time

Usage:

- Select the input for waiting time by sliding the bar
- The app will predict the eruption duration and output the result
- You can show/hide prediction line by checking/unchecking the show box